---
title: "Assignment"
output: html_document
---
Loading the data into R and making sure that it reads dates as dates.
```{r}
library(data.table)
activity <- read.csv("C:/Users/Miro/Documents/Reproducible Research/repdata_data_activity/activity.csv", 
                     header = TRUE, sep = ",")

activity$date <- as.Date(activity$date)
```

Now grouping steps by intervals. (And loading package dplyr).

```{r}
library(dplyr)
stepsperday <- activity %>% 
  group_by(date) %>% 
  summarize(TotalSteps=sum(steps))
```

Now, grouped, make a histogram.

```{r}
hist(stepsperday$TotalSteps, main = "Steps and how many there are each day", xlab = "All the STEEEPS Per day", ylab = "the Count of spets")
```

Completing steps and calculating the mean and the median.
```{r}
SomeStepsPerDay <- stepsperday[complete.cases(stepsperday), ]
meanofsteps <- mean(SomeStepsPerDay$TotalSteps)
medianofsteps <-median(SomeStepsPerDay$TotalSteps)
```

Complete cases in the original datasets and making a datset grouped by interval and average number of steps taken. Then plotting it.  
```{r}
activity <- activity[complete.cases(activity), ]
timesteps <- group_by(activity, interval) %>%
summarise(AverageSteps=mean(steps))
plot(timesteps$interval, timesteps$AverageSteps, 
      type = "b", xlab = "Time Interval", ylab = "Steps", main = "average steps in time")
```

Finding the maximum interval
```{r}
MaximumStepInterval <- timesteps$interval[which.max(timesteps$AverageSteps)]
```

Loading in data again to have raw data
``` {r}
rawactivity <- read.csv("C:/Users/Miro/Documents/Reproducible Research/repdata_data_activity/activity.csv", 
                     header = TRUE, sep = ",")
```

Filling in missing data

```{r}
fillrawdata <- rawactivity
for (i in 1:nrow(fillrawdata)) {
  if (is.na(fillrawdata$steps[i])) {
    ndx <- which(fillrawdata$interval[i] == timesteps$interval)
    fillrawdata$steps[i] <- timesteps[ndx,]$AverageSteps
  }
}
```

Grouping by date and making total number of steps after missing values were imputed.
```{r}
fillrawdatasteps <- fillrawdata %>% 
  group_by(date) %>% 
  summarize(TotalSteps=sum(steps))
hist(fillrawdatasteps$TotalSteps, main = "Steps and how many there are each day", xlab = "All the STEEEPS Per day", ylab = "the Count of spets")
```

Making sure the date in the new raw data is read as date, then defining what is a weekday and whats a weekend. 
``` {r}
fillrawdata$date <- as.Date(fillrawdata$date)
fillrawdata$day <- weekdays(fillrawdata$date)
fillrawdata$day[fillrawdata$day %in% c("Saturday", "Sunday")] <- "weekend"
fillrawdata$day[fillrawdata$day %in% c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")] <- "weekday"
```

Using the new data to group it by weekday, interval and calculate the total steps per day. 
``` {r}
fillrawdataday <- fillrawdata %>% 
  group_by(day, interval) %>% 
  summarize(TotalSteps=sum(steps))
```

Npw subsetting the dataset into two new datasets - one for weekdays and the other for weekends.
```{r}
fillrawdataweekend <- subset(fillrawdataday, day == "weekend")
fillrawdataweekday <- subset(fillrawdataday, day == "weekday")
```

Now plotting two graphs by weekends and weekdays. 
``` {r}
plot(fillrawdataweekend$TotalSteps, type = "l", xlab = "Weekends", ylab = "Steps", main = "Steps in weekends")
plot(fillrawdataweekday$TotalSteps, type = "l", xlab = "Weekdays", ylab = "Steps", main = "Steps in weekdays")
```
